--- 
title: "MSc. Data Science - Research Proposal"
subtitle: "LJMU | UPGRAD - Batch 2019"
author: "Thabor Walbeek"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Research proposal for the master thesis of the MSc. Data Science"
---

# To be removed | Bookdown eplanation

This is a _sample_ research proposal written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

More explanation about **bookdown** can be found at: <https://bookdown.org/yihui/bookdown/usage.html>

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE, include = FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
